### 2017-04-06 sections/implementation.tex
Update on Overleaf.

Storage size of SVD decomposition itself can also be optimized. $\mtrx{\Sigma}$ being a diagonal matrix can be stored as single list of singular values $\sigma_{i}$ or can be even multiplied with the matrix of left singular vectors $\mtrx{U}$.

>>>>

Storage size of SVD decomposition itself can also be optimized. $\mtrx{S}$ being a diagonal matrix can be stored as single list of singular values $\sigma_{i}$ or can be even multiplied with the matrix of left singular vectors $\mtrx{U}$.
